---
title: 'DKDL model v2.0 partykit version'
author: "Gertjan Verhoeven"
date: "10/7/2023"
output:
  pdf_document: default
  html_document: default
editor_options:
  chunk_output_type: inline
---

This notebook showcases the final DKDL model implemented as a partykit model.
This model can be used as a reference implementation, or as a backend in apps.

The partykit model "dkdl" consists of three R files.
`partykit_dkdl.R` contains the caret wrapper for training (fitting) the model to data.
`dkdl_model.R` contains the full node structure of the decision tree.
`dkdl_splits.R` contains the split functions that partition the data while it descends down into the node structure.

The model is developed as a regression tree.

# Load packages

```{r}
library(partykit)
library(data.table)
library(tidyverse)
library(caret)
```



## Simulate fake data

```{r}
source("partykit_dkdl.R")
```


```{r}
source("dataprep_fake_dkdl.R")

df_orig <- df
```

Convert df to subset needed for the DKDL model.

```{r}
col_names <- c("VR_verloop.4", 
                    "VR_technisch_infuusbehandeling",
                    "DK",
                    "DL",
                    "OB",
                    "y")

df <- df_orig %>% select(all_of(col_names))
```


## Caret

```{r}
fitControl <- trainControl(method = "repeatedcv",
                           repeats = 1,
                           verboseIter = FALSE)
```

```{r}
set.seed(123)
my_formula <- as.formula(paste("y ~ ."))

pk.fit <- train(my_formula, 
                data = df, 
                         method = partykit_dkdl, 
                         trControl = fitControl)

df$cluster_id <- predict(pk.fit$finalModel, type = "node")
pk.fit
```

```{r}
df <- add_cluster_labels(df, modelNaam = "Draagkracht/draaglast model variant3",
                         config_dir = "../../config/")

table(df$cluster_id)
```
```{r}
res <- df %>%
    group_by(cluster_sort_nr, hoofd_categorie, subgroep, categorie_soort, categorie_soort_sort_order
) %>%
    summarise(perc_clienten = round(n()/nrow(df), 3),
              n_obs = n(), 
              avg_uren = round(mean(y),1))

```

```{r fig.width = 15, fig.height=10}
source("dkdl_model.R")



treemodel <- party(pn, data = df, 
                   fitted = data.frame("(fitted)" = fitted_node(pn, data = df),
                                       "(response)" = df$y,
                                       check.names = FALSE), # needed for the funky names
                   terms = terms(AvgDuurWtd_4 ~ ., data = df) # model formula
)

treemodel <- as.constparty(treemodel)

treemodel
```

